THESIS PROJECT PROPOSAL

### 2019-11-21 project_ashish/paper.tex

\onehalfspacing The research project propose to study the unobserved production channel of the Higgs boson in associated with a single top quark (tH) using Higgs boson decay to multilepton final state. The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$. Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode. The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations. Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb. We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$. \par

>>>>

\onehalfspacing This research project proposes to study the unobserved production channel of the Higgs boson in associated with a single top quark (tH) using Higgs boson decay to multilepton final state. The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$. Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode. The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations. Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb. We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$. \par
